Reproducible, flexible and high throughput data extraction from primary literature: The metaDigitise R package

### 2017-10-31 docs/manuscript.tex
manuscript editing

\title{Flexible, high throughput data extraction from primary literature: The metaDigitise R package}
\author{? Joel L. Pick ?...? \& Daniel W.A. Noble ?}
% \date{}

@@

It then prompts the user to select whether they want to extract from new images, import previously extracted data or edit previously extracted data. Extracting from new images takes the user through the steps outlined below, figure by figure, giving the user the option to quit the process after each figure. If this process has already been started when the user starts metaDigitise, then it starts where the user left off. Similarly if the user adds new images to the parent directory after all other images are extracted (or part way through), the new images will be extracted from. After extraction (or upon quitting the function), the extracted data will be returned. %% explain summary etc

@@

\subsection{Figure Rotation}
Figure may have been extracted from old publications, for example from scanned images, and so are not perfectly orientated on the image. This will make the calibration of the points in the figure from the image problematic. metaDigitise allows users to rotate the image. By clicking two points on the x-axis, metaDigitse calculates the angle needed to rotate the image so the x-axis is horizontal, and rotates it. (Figure \ref{fig:rotate} )

\begin{figure}[!h] 
%\onehalfspacing
 \includegraphics[width=0.9\textwidth]{fig_rotate.pdf} 
 \caption{ }
\label{fig:rotate}
\end{figure}

Furthermore, in some figures mean and error, boxplots or histograms may be presented with horizontal bars. metaDigitise assumes that the bars are vertical, but allows the user to flip the image so that the bars are vertical (Figure \ref{fig:flip}).

\begin{figure}[!h] 
%\onehalfspacing
 \includegraphics[width=0.9\textwidth]{fig_flip.pdf} 
 \caption{ }
\label{fig:flip}
\end{figure}

@@

\begin{figure}[!h] 
%\onehalfspacing
 \includegraphics[width=0.9\textwidth]{fig_calibrate.pdf} 
 \caption{ }
\label{fig:calibrate}
\end{figure}

@@

\subsubsection{Mean and error plots} 
metaDigitise prompts the user to enter groups names and allows the user to enter sample sizes, which are used in downstream processing. The user is then prompted to click on an error bar followed by the mean. Error bars above or below the mean can be clicked - sometimes one is clearer than the other. metaDigitise assumes that the error bars are symmetrical. Where the user has clicked the error is displayed in a different colour to the mean. The user can subsequently add more groups or remove groups.

\begin{figure}[!h] 
%\onehalfspacing
 \includegraphics[width=0.9\textwidth]{fig_all_extract.pdf} 
 \caption{ }
\label{fig:all_extract}
\end{figure}

@@

\subsubsection{Scatter plots}
 metaDigitise prompts the user to enter groups names and then to click on points. Points added by mistake can be deleted. The user can subsequently add groups, edit groups (add or remove points) or delete groups. Different groups are plotted in different colours and shapes, with a legend at the bottom of the figure (Figure \ref{fig:scatter_points}. The x and y coordinates are returned.

\begin{figure}[!h] 
%\onehalfspacing
 \includegraphics[width=0.9\textwidth]{fig_scatter_points.pdf} 
 \caption{ }
\label{fig:scatter_points}
\end{figure}

@@

>>>>

\title{Reproducible, flexible and high throughput data extraction from primary literature: The metaDigitise R package}
\author{? Joel L. Pick ?...? \& Daniel W.A. Noble ?}
% \date{}

@@

It then prompts the user to select whether they want to extract from new images, import previously extracted data or edit previously extracted data. Extracting from new images takes the user through the steps outlined below, figure by figure, giving the user the option to quit the process after each figure. If this process has already been started when the user starts metaDigitise, then it starts where the user left off. Similarly if the user adds new images to the parent directory after all other images are extracted (or part way through), the new images will be integrated into the extraction procedure. After extraction (or upon quitting the function), the extracted data will be returned. %% explain summary etc

@@

\subsection{Figure Rotation}
Figure may have been extracted from old publications, for example from scanned images, and so are not perfectly orientated on the image. This will make the calibration of the points in the figure from the image problematic. metaDigitise allows users to rotate the image. By clicking two points on the x-axis, metaDigitse calculates the angle needed to rotate the image so the x-axis is horizontal, and rotates it. (Figure \ref{fig:rotate}A,B)

\begin{figure}[!h] 
%\onehalfspacing
 \includegraphics[width=0.9\textwidth]{fig_rotate.pdf} 
 \caption{Figure rotation. A) and B) show how non-aligned imaged can be realigned through user defined rotation. C) and D) show show figures can be re-orientated so as to aid data input.}
\label{fig:rotate}
\end{figure}

Furthermore, in some figures mean and error, boxplots or histograms may be presented with horizontal bars. metaDigitise assumes that the bars are vertical, but allows the user to flip the image so that the bars are vertical (Figure \ref{fig:rotate}C,D).

@@

\begin{figure}[!h] 
%\onehalfspacing
 \includegraphics[width=0.9\textwidth]{fig_calibrate.pdf} 
 \caption{Axis calibration. The user defines two points on each axis and labels them according to the values shown in the figure.}
\label{fig:calibrate}
\end{figure}

@@

\begin{figure}[!h] 
%\onehalfspacing
 \includegraphics[width=0.9\textwidth]{fig_all_extract.pdf} 
 \caption{Demonstration of data extraction from different plot types}
\label{fig:all_extract}
\end{figure}

\subsubsection{Mean and error plots} 
metaDigitise prompts the user to enter groups names and allows the user to enter sample sizes, which are used in downstream processing. The user is then prompted to click on an error bar followed by the mean. Error bars above or below the mean can be clicked - sometimes one is clearer than the other. metaDigitise assumes that the error bars are symmetrical. Where the user has clicked the error is displayed in a different colour to the mean (Figure \ref{fig:all_extract}A). The user can subsequently add more groups or remove groups.

@@

\subsubsection{Scatter plots}
 metaDigitise prompts the user to enter groups names and then to click on points. Points added by mistake can be deleted. The user can subsequently add groups, edit groups (add or remove points) or delete groups. Different groups are plotted in different colours and shapes, with a legend at the bottom of the figure (Figure \ref{fig:all_extract}C). The x and y coordinates are returned.

@@

\section{Example}
%% scatterplot from airquality data

\section{Testing}
%% simulated data
%% x people doing y plots
